---
title: "Cleaning"
author: "Guiquan"
date: "2021/5/3"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data preparation, multiple imputation and some EDA analysis.

# Data Preparation
```{r}
library(tidymodels)
# Preparation of original data
original <- openxlsx::read.xlsx("original_derivation.xlsx", detectDates = TRUE) %>% 
  as_tibble() %>% 
  mutate_if(is.character, as.factor)
original_amp <- original %>% 
  select(-c(ID, Optime, PRL, T, TC, TG, LDL, HDL, HCY, CA125, Insulin, BUN, FBG, BMI, A.panicillin, A.cepha, NG.DNA, UUorMH.DNA, Rh_neg, Num.pretrigger))
set.seed(777)
porsm_split_amp <- initial_split(original_amp, strata = POR, prop = 0.7)
porsm_train_amp <- training(porsm_split_amp)
porsm_test_amp <- testing(porsm_split_amp)
horsm_split_amp <- initial_split(original_amp, strata = HOR, prop = 0.7)
horsm_train_amp <- training(horsm_split_amp)
horsm_test_amp <- testing(horsm_split_amp)
```

# EDA analysis
## Prerequisites
```{r}
library(tidyverse)
library(VIM)
library(ggcorrplot)
library(gridExtra)
library(compareGroups)
```

## Missing data exploration
```{r}
# Missing proportion
naniar::miss_var_summary(original) %>% mutate(pct_miss = round(pct_miss, 2)) %>% 
  openxlsx::write.xlsx("inclusion and exclusion of initial covariates.xlsx")
```

# Multiple imputation of The Original Data using random forest based MICE.
## Imputing missing data
```{r}
library(miceRanger)
porsm_train_miceObj <- miceRanger(
  porsm_train_amp,
  m = 1,
  maxiter = 100,
  valueSelector = "meanMatch",
  meanMatchCandidates = 5, 
  seed = 777)
porsm_test_miceObj <- miceRanger(
  porsm_test_amp,
  m = 1,
  maxiter = 100,
  valueSelector = "meanMatch",
  meanMatchCandidates = 5, 
  seed = 777)
horsm_train_miceObj <- miceRanger(
  horsm_train_amp,
  m = 1,
  maxiter = 100,
  valueSelector = "meanMatch",
  meanMatchCandidates = 5, 
  seed = 777)
horsm_test_miceObj <- miceRanger(
  horsm_test_amp,
  m = 1,
  maxiter = 100,
  valueSelector = "meanMatch",
  meanMatchCandidates = 5, 
  seed = 777)
```

## Diagnostic plotting
```{r}
plotDistributions(miceObj, vars = c("FSH", "LH", "E", "P", "AMH", "TP", "ALB", "ALT", "AST", "Cr", "RBC", "WBC", "PT", "APTT", "AFC"), ncol = 5, nrow = 3)
plotCorrelations(miceObj, vars = "allNumeric", ncol = 5, nrow = 3)
plotVarConvergence(miceObj, vars = "allNumeric", ncol = 5, nrow = 3)
plotModelError(miceObj, vars = "allNumeric", ncol = 5, nrow = 3)
plotImputationVariance(miceObj)
```

## Preparation of the imputed derivation data.
```{r}
porsm_train <- completeData(porsm_train_miceObj) %>% 
  map_df(tibble) %>% select(-c(Num.oocytes, HOR))
porsm_test <- completeData(porsm_test_miceObj) %>% 
  map_df(tibble) %>% select(-c(Num.oocytes, HOR))
porsm_data <- bind_rows(porsm_train, porsm_test)

horsm_train <- completeData(horsm_train_miceObj) %>% 
  map_df(tibble) %>% select(-c(Num.oocytes, POR))
horsm_test <- completeData(horsm_test_miceObj) %>% 
  map_df(tibble) %>% select(-c(Num.oocytes, POR))
horsm_data <- bind_rows(horsm_train, horsm_test)
```

## Baseline characteristics table (original vs. imputed).
```{r}
compareGroups::descrTable(data = original_amp %>% select(c(AMH, P, E, AFC, Duration, FSH, LH, RBC, WBC, HCT, Ct.DNA, Men.frequency, DBP, SBP, Cr, PT, APTT, Menarche, ABO, ALB, AST, TP, Abnormal.his, Men.regularity, ALT, PLT, Hb, Education, Pri.Sec)), 
                          method = NA,
                          show.all = TRUE,
                          digits = 2)

compareGroups::descrTable(data = porsm_data %>% select(c(AMH, P, E, AFC, Duration, FSH, LH, RBC, WBC, HCT, Ct.DNA, Men.frequency, DBP, SBP, Cr, PT, APTT, Menarche, ABO, ALB, AST, TP, Abnormal.his, Men.regularity, ALT, PLT, Hb, Education, Pri.Sec)),
                          method = NA,
                          show.all = TRUE,
                          digits = 2)

compareGroups::descrTable(data = horsm_data %>% select(c(AMH, P, E, AFC, Duration, FSH, LH, RBC, WBC, HCT, Ct.DNA, Men.frequency, DBP, SBP, Cr, PT, APTT, Menarche, ABO, ALB, AST, TP, Abnormal.his, Men.regularity, ALT, PLT, Hb, Education, Pri.Sec)),
                          method = NA,
                          show.all = TRUE,
                          digits = 2)
```

## Baseline characteristics table (original vs. validation).
```{r}
compareGroups::descrTable(Cat.oocytes ~ ., 
                          data = original_amp %>% 
                            select(Age, Duration, Weight, DBP, FSH, LH, P, WBC, RBC, PLT, ALT, AMH, AFC, POIorDOR, PCOS, Protocol, Initial.FSH, Recombinant, Use.LH, Num.oocytes) %>% 
                            mutate(Cat.oocytes = case_when(Num.oocytes < 4 ~ "Poor",
                                                           Num.oocytes > 20 ~ "High",
                                                           TRUE ~ "Normal")) %>% 
                            mutate_if(is.character, as.factor), 
                          method = NA,
                          show.all = TRUE, 
                          digits = 1) 

ningbo_baseline <- openxlsx::read.xlsx("validation for OR.xlsx", detectDates = TRUE) %>% 
  select(Age, Duration, Weight, DBP, FSH, LH, P, WBC, RBC, PLT, ALT, AMH, AFC, POIorDOR, PCOS, Protocol, Initial.FSH, Recombinant, Use.LH, Num.oocytes, Cat.oocytes) %>% 
  mutate_if(is.character, as.factor) %>% 
  filter(if_all(everything(), ~ !is.na(.x)))
compareGroups::descrTable(Cat.oocytes ~ ., 
                          data = ningbo_baseline,
                          method = NA,
                          show.all = TRUE,
                          digits = 2) 
```



















